---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = NULL
)
Sys.setlocale("LC_MESSAGES", 'en_GB.UTF-8') # Force locale
```

# ananke

<!-- badges: start -->
[![R-CMD-check](https://github.com/tesselle/ananke/workflows/R-CMD-check/badge.svg)](https://github.com/tesselle/ananke/actions)
[![codecov](https://codecov.io/gh/tesselle/ananke/branch/main/graph/badge.svg?token=UgoOXsZW86)](https://app.codecov.io/gh/tesselle/ananke)
[![CodeFactor](https://www.codefactor.io/repository/github/tesselle/ananke/badge/main)](https://www.codefactor.io/repository/github/tesselle/ananke/overview/main)

[![r-universe](https://tesselle.r-universe.dev/badges/ananke)](https://tesselle.r-universe.dev/ananke){.pkgdown-devel}

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)

[![DOI Zenodo](https://zenodo.org/badge/DOI/10.5281/zenodo.13236285.svg)](https://doi.org/10.5281/zenodo.13236285)
<!-- badges: end -->

## Overview

**ananke** provides functions for simple radiocarbon calibration and chronological analysis.

---

```{r citation, echo=FALSE, comment='', results='asis'}
cite <- utils::citation("ananke")
print(cite, bibtex = FALSE)
```

## Installation

You can install the released version of **ananke** from [CRAN](https://CRAN.R-project.org) with:

```{r cran-installation, eval=FALSE}
install.packages("ananke")
```

And the development version from [GitHub](https://github.com/) with:

```{r gh-installation, eval=FALSE}
# install.packages("remotes")
remotes::install_github("tesselle/ananke")
```

## Usage

```{r packages-load}
## Load packages
library(ananke)
```

```{r calibration, fig.width=7, fig.height=7}
## Data from Bosch et al. 2015
data("ksarakil")

## Calibrate multiple dates
cal <- c14_calibrate(
  values = ksarakil$date,
  errors = ksarakil$error,
  names = ksarakil$code,
  curves = "marine13",
  reservoir_offsets = 53,
  reservoir_errors = 43,
  from = 50000, to = 0
)

## Plot
plot(cal)

## Full text description
describe(cal, fill = TRUE)
```

## Related Works

* [**Bchron**](https://github.com/andrewcparnell/Bchron) enables quick calibration of radiocarbon dates, age-depth modelling, relative sea level rate estimation, and non-parametric phase modelling.
* [**racarbon**](https://github.com/ahb108/rcarbon) includes functions not only for basic calibration, uncalibration, and plotting of one or more dates, but also a statistical framework for building demographic and related longitudinal inferences from aggregate radiocarbon date lists.
* [**rintcal**](https://github.com/Maarten14C/rintcal) consists of a data compilation of the IntCal radiocarbon calibration curves and provides a number of functions to assist with calibrating dates and plotting calibration curves.

## Contributing

Please note that the **ananke** project is released with a [Contributor Code of Conduct](https://www.tesselle.org/conduct.html). By contributing to this project, you agree to abide by its terms.
