---
output: github_document
bibliography: vignettes/bibliography.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = NULL
)
```

# ananke

<!-- badges: start -->
[![R-CMD-check](https://github.com/tesselle/ananke/workflows/R-CMD-check/badge.svg)](https://github.com/tesselle/ananke/actions)
[![codecov](https://codecov.io/gh/tesselle/ananke/branch/main/graph/badge.svg)](https://app.codecov.io/gh/tesselle/ananke)
[![CodeFactor](https://www.codefactor.io/repository/github/tesselle/ananke/badge/main)](https://www.codefactor.io/repository/github/tesselle/ananke/overview/main)
[![Dependencies](https://tinyverse.netlify.com/badge/ananke)](https://cran.r-project.org/package=ananke)

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

## Overview

A toolkit for temporal reasoning. **ananke** allows to describe and analyze finite time intervals. It includes tools for radiocarbon calibration and Bayesian chronological modeling. It also provides classes and methods for the representation of archaeological sequence diagrams in the framework of @dye2015.

## Installation

You can install the released version of **ananke** from [CRAN](https://CRAN.R-project.org) with:

```{r cran-installation, eval=FALSE}
install.packages("ananke")
```

And the development version from [GitHub](https://github.com/) with:

```{r gh-installation, eval=FALSE}
# install.packages("remotes")
remotes::install_github("tesselle/ananke")
```

## Contributing

Please note that the **ananke** project is released with a [Contributor Code of Conduct](https://www.tesselle.org/conduct.html). By contributing to this project, you agree to abide by its terms.

## References
