---
output: github_document
bibliography: inst/bibliography.bib
nocite: '@*'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = NULL
)
Sys.setenv(LANGUAGE = "en") # Force locale
```

# ananke

<!-- badges: start -->
[![Code coverage](https://packages.tesselle.org/ananke/coverage/badge.svg)](https://packages.tesselle.org/ananke/coverage/)
[![r-universe](https://tesselle.r-universe.dev/badges/ananke)](https://tesselle.r-universe.dev/ananke){.pkgdown-devel}

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)

[![DOI Zenodo](https://zenodo.org/badge/DOI/10.5281/zenodo.13236285.svg)](https://doi.org/10.5281/zenodo.13236285)
<!-- badges: end -->

## Overview

**ananke** provides functions for simple radiocarbon calibration and chronological analysis.

This package is currently *experimental*. This means that it is functional, but interfaces and functionalities may change over time, testing and documentation may be lacking.

---

```{r citation, echo=FALSE, comment='', results='asis'}
cite <- utils::citation("ananke")
print(cite, bibtex = FALSE)
```

## Installation

You can install the released version of **ananke** from [CRAN](https://CRAN.R-project.org) with:

```{r cran-installation, eval=FALSE}
install.packages("ananke")
```

And the development version from [Codeberg](https://codeberg.org/) with:

```{r gh-installation, eval=FALSE}
# install.packages("remotes")
remotes::install_git("https://codeberg.org/tesselle/ananke")
```

## Usage

```{r packages-load}
## Load packages
library(ananke)
```

**ananke** uses [**aion**](https://packages.tesselle.org/aion/) for internal date representation. Look at `vignette("aion", package = "aion")` before you start.

```{r calibration, fig.width=7, fig.height=7}
## Data from Bosch et al. 2015
data("ksarakil")

## Calibrate multiple ages
cal <- c14_calibrate(
  values = ksarakil$date,
  errors = ksarakil$error,
  names = ksarakil$code,
  curves = "marine13",
  reservoir_offsets = 53,
  reservoir_errors = 43,
  from = 50000, to = 0
)

## Plot
plot(cal)
```

## Translation

This package provides translations of user-facing communications, like messages, warnings and errors, and graphical elements (axis labels). The preferred language is by default taken from the locale. This can be overridden by setting of the environment variable `LANGUAGE` (you only need to do this once per session):

``` r
Sys.setenv(LANGUAGE = "<language code>")
```

Languages currently available are English (`en`) and French (`fr`).

## Related Works

* [**Bchron**](https://github.com/andrewcparnell/Bchron) enables quick calibration of radiocarbon dates, age-depth modelling, relative sea level rate estimation, and non-parametric phase modelling.
* [**rcarbon**](https://github.com/ahb108/rcarbon) includes functions not only for basic calibration, uncalibration, and plotting of one or more dates, but also a statistical framework for building demographic and related longitudinal inferences from aggregate radiocarbon date lists.
* [**rintcal**](https://github.com/Maarten14C/rintcal) consists of a data compilation of the IntCal radiocarbon calibration curves and provides a number of functions to assist with calibrating dates and plotting calibration curves.

## Contributing

Please note that the **ananke** project is released with a [Contributor Code of Conduct](https://www.tesselle.org/conduct.html). By contributing to this project, you agree to abide by its terms.

## References

```{r metadata, include=FALSE}
## Update codemeta.json
codemetar::write_codemeta(verbose = FALSE)

## Update CITATION.cff
cff_keys <- list(
  identifiers = list(
    list(description = "The concept DOI.",
         type = "doi",
         value = "10.5281/zenodo.13236285"),
    list(description = "The versioned DOI for version 0.0.1.",
         type = "doi",
         value = "10.5281/zenodo.13236286")
  )
)
cff <- cffr::cff_create("DESCRIPTION", keys = cff_keys)
if (cffr::cff_validate(cff)) cffr::cff_write(cff, outfile = "CITATION.cff")
```
